API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Introduce supervised learning, classification and regression

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a pair of
values $([x_1,..., x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrix with numerical values: one for the input
values and one for the output values. Each row of these matrix
corresponds to one sample of the dataset and each column to one variable of
the problem.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example in supervised learning task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some discrete as in classification task or continous as in regression task
output variables $Y$. A sample is then defined as a pair of
values $([x_1,..., x_p]^\mathrm{T}, y)$ of these variables. A widely used
representation of a dataset, a collection of
such samples, is a pair of matrices with numerical values: one for the input
values and one for the output values. Each row of these matrices
corresponds to one sample of the dataset and each column to one variable of
the problem.
